### 2021-10-28 manuscript/hiv-gwas.tex
Update on Overleaf.

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=\linewidth]{figures/200207_gwas_results}
		\caption{Association results for standard GWAS and GWAS with a phylogenetic correction applied to the same data for HIV-1 set-point viral load. The pullout plots give regional association results from the GWAS with phylogenetic correction in the \emph{CCR5} region (positions 45.4 - 47Mb on chromosome 3) and the MHC region (positions 29.5 - 33.5Mb on chromosome 6). Base positions are with reference to genome build GRCh37. The color scale in the regional association plot is the difference in -log$_{10}$ p-value between the GWAS with phylogenetic correction and the standard GWAS. Red color means the phylogenetic correction decreased variant significance and blue color means the phylogenetic correction increased variant significance. The dashed lines show genome-wide significance (p-value = 5x10$^{-8}$).}
		\label{fig:gwas-results}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.75\textwidth}
		\includegraphics[width=\linewidth]{figures/200207_POUMM_posteriors_zoomed.png}
		\caption{Marginal posterior distributions.}
	\end{subfigure}
~
	\begin{subfigure}[b]{0.75\textwidth}
		\includegraphics[width=\linewidth]{figures/200207_POUMM_traces.png}
		\caption{MCMC trace plots.}
	\end{subfigure}
	\caption{POUMM parameter inference.}\label{fig:poumm-fit}
\end{figure}

\begin{figure}
	\includegraphics[width=\linewidth]{figures/200207_spvl_on_tree}
	\caption{Inferred viral phylogeny with tips colored by estimated viral part of spVL, non-viral part of spVL, and measured total spVL.}
	\label{fig:spvl-on-tree}
\end{figure}

@@

\begin{table}[H]
	\begin{center}
		\begin{tabular}{lc}
			\hline
			Variant filter & Number of variants remaining \\
			\hline 
			Raw data & 76,979,521 \\
			Missing call rate $>$ 0.01 & -69,526,564 \\
			Hardy-Weinburg p-value $<$ 5x10$^-5$ & -535 \\
			Minor allele frequency $<$ 0.01 & -2,897,654 \\
			Variants for GWAS & 4,554,768 \\ \hline			
		\end{tabular}
		\caption{Number of variants for GWAS after sequential filtering steps.}
		\label{tab:variant-filtering}
	\end{center}
\end{table}

\begin{figure}[H]
	\includegraphics[width=\linewidth]{figures/pca_plot}
	\caption{Thresholds for exclusion of individuals of non-Western European ancestry. The lower plots are filtered to show only European HapMap samples and the rectangles show thresholds for sample exclusion.}
	\label{fig:PCA}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.75\linewidth]{figures/200207_qq_plots.png}
	\caption{Quartile-quartile plots from association tests.}
	\label{fig:qq-plots}
\end{figure}

>>>>

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=\linewidth]{figures_archived/200207_gwas_results}
		\caption{Association results for standard GWAS and GWAS with a phylogenetic correction applied to the same data for HIV-1 set-point viral load. The pullout plots give regional association results from the GWAS with phylogenetic correction in the \emph{CCR5} region (positions 45.4 - 47Mb on chromosome 3) and the MHC region (positions 29.5 - 33.5Mb on chromosome 6). Base positions are with reference to genome build GRCh37. The color scale in the regional association plot is the difference in -log$_{10}$ p-value between the GWAS with phylogenetic correction and the standard GWAS. Red color means the phylogenetic correction decreased variant significance and blue color means the phylogenetic correction increased variant significance. The dashed lines show genome-wide significance (p-value = 5x10$^{-8}$).}
		\label{fig:gwas-results}
	\end{center}
\end{figure}

@@

\begin{figure}[H]
	\centering
		\includegraphics[width=\linewidth]{figures/poumm_parameter_estimates.png}
		\caption{Marginal posterior distributions.}
\label{fig:poumm-parameters}
\end{figure}

\begin{figure}
\includegraphics[width = 0.3\linewidth]{figures/pathogen_tree_with_trait.png}
\includegraphics[width = 0.3\linewidth]{figures/pathogen_tree_with_phylo-estimated_env_trait.png}
\includegraphics[width = 0.3\linewidth]{figures/pathogen_tree_with_phylo-estimated_pathogen_trait.png}
	\caption{Inferred viral phylogeny with tips colored by measured total spVL, estimated non-viral part of spVL, and estimated viral part of spVL.}
	\label{fig:spvl-on-tree}
\end{figure}

@@

\begin{table}[H]
	\begin{center}
		\begin{tabular}{lc}
			\hline
			Variant filter & Number of variants remaining \\
			\hline 
			Raw data & 76979521 \\
			Missing genotype rate $>$ 0.01 & 7452957 \\
			Hardy-Weinburg exact test p-value $<$ 5x10$^-5$ & 7452425 \\
			Minor allele frequency $<$ 0.01 & 4556770 \\ \hline			
		\end{tabular}
		\caption{Number of variants for GWAS after sequential filtering steps.}
		\label{tab:variant-filtering}
	\end{center}
\end{table}

\begin{figure}[H]
	\includegraphics[width=\linewidth]{figures/host_genotype_pca.png}
	\caption{SHCS individuals and HapMap3 individuals plotted along the top three principle components of genetic variation. Points with black borders are within the thresholds used to select individuals of likely European ancestry.}
	\label{fig:PCA}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.75\linewidth]{figures_archived/200207_qq_plots.png}
	\caption{Quartile-quartile plots from association tests.}
	\label{fig:qq-plots}
\end{figure}
